Draft

### 2020-08-29 Final.Rmd
minor text adjustments. fixed the margin problem of inserted pdf figures.

\begin{align}
\boldsymbol{{\hat \theta}^{[i]}}:=arg\max_{\boldsymbol{\theta \in \Theta}}\bar S_i({\boldsymbol\theta})
\end{align}
\begin{align}
\bar S_i(\boldsymbol\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S(P_{\boldsymbol\theta}^{t-1},y_t)
\end{align}
  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$ And compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to (11)(12)(13):

@@

@@

# put two plots side by side 
ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 4(a) Lower Tail","Figure 4(b) Upper Tail"))

@@

1. Using the sequence of predictive densities (p) produced by {LS, CRPS, FSR10, FSR20, FSR80, FSR90} in Section 3:

    (a) $p_{LS}(y_{1001}|y_{1000})...p_{LS}(y_{5000}|y_{4999})$;
    (b) $p_{CRPS}(y_{1001}|y_{1000})...p_{CRPS}(y_{5000}|y_{4999})$
    (c) $p_{FSR10}(y_{1001}|y_{1000})...p_{FSR10}(y_{5000}|y_{4999})$
    (d) $p_{FSR20}(y_{1001}|y_{1000})...p_{FSR20}(y_{5000}|y_{4999})$
    (e) $p_{FSR80}(y_{1001}|y_{1000})...p_{FSR80}(y_{5000}|y_{4999})$
    (f) $p_{FSR90}(y_{1001}|y_{1000})...p_{FSR90}(y_{5000}|y_{4999})$

@@

# put two plots side by side 
ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 6(a) Lower Tail","Figure 6(b) Upper Tail"))

@@

# put two plots side by side 
ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 7(a) Lower Tail","Figure 7(b) Upper Tail"))
```

@@

# put two plots side by side 
ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 8(a) Lower Tail","Figure 8(b) Upper Tail"))

@@

# put two plots side by side 
ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 9(a) Lower Tail","Figure 9(b) Upper Tail"))

>>>>

\begin{align}
\boldsymbol{{\hat \theta}^{[i]}}:=arg\max_{\boldsymbol{\theta \in \Theta}}\bar S_i({\boldsymbol\theta})
\end{align}
\begin{align}
\bar S_i(\boldsymbol\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S(P_{\boldsymbol\theta}^{t-1},y_t)
\end{align}
  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$, and compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to (11)(12)(13):

@@

```{r,fig.align="center"}
knitr::include_graphics("figure_pred.pdf")
```

@@

# put two plots side by side 
ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 4(a) 10 percentile","Figure 4(b) 90 percentile"))

@@

1. Using the sequence of predictive densities (p) produced by $S_i$ in Section 3:

- $S_i= \{LS, CRPS, FSR10, FSR20, FSR80, FSR90\}$;

- Conditional out-of-sample predictives: $p_{S_i}(y_{1001}|y_{1000})...p_{S_i}(y_{5000}|y_{4999})$;

@@

# put two plots side by side 
ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 6(a) 10 percentile","Figure 6(b) 90 percentile"))

@@

# put two plots side by side 
ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 7(a) 10 percentile","Figure 7(b) 90 percentile"))
```

@@

# put two plots side by side 
ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 8(a) 10 percentile","Figure 8(b) 90 percentile"))

@@

# put two plots side by side 
ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 9(a) 10 percentile","Figure 9(b) 90 percentile"))
